---
title: "Building clustering"
author: "Joan Claverol Romero"
date: "02/12/2019"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, message = F, warning = F)
# libraries
if (require(pacman) == FALSE) {
  install.packages("pacman")
}
pacman::p_load(tidyverse, magrittr, kableExtra, knitr, caret)

# setting visualization themes ggplot
theme_set(theme_bw())
```

## GOAL

Use techniques like:

* k-means
* dendogram
* PCA

To find the closer waps to predict the buildings. 

First we will use latitude and longitude, and then only the WAPs information. 

## Load data

We will use for the moment the traian data. We will load the rds file preparated by the files `preparation_rds.R`:

```{r}
train <- read_rds("../../data/clean/train.rds")
```

Let's see if we can use clustering techniques: 

```{r}
train_gath <- train %>% 
  # gather the WAPS to two columns: WAPs and their values
  pivot_longer(cols = starts_with("WAP"), names_to = "WAPs") %>% 
  select(LONGITUDE, LATITUDE, BUILDINGID, WAPs, value, PHONEID) %>% 
  filter(value != 100)
```

Do we have duplicates inside our data?

* Now the dataset contains `r nrow(train_gath)`. Let's take out the duplicates. 

```{r}
train_unique <- train_gath %>% 
  filter(value != 100) %>% # filter out the non detected WAPs
  distinct_all(.keep_all = T) # Make sure we have unique observations
```

Now our dataset has been reduced to `r nrow(train_gath)`. As our first step will be to create cluster by latitude and longitude, we will not use the WAPs value. We will use k-mean forr the first approach. 

As we want to detect the 3 main buildings, we will define as k = 3. 

```{r}
# define set seed and apply the k-means
set.seed(45)
k <- 6 # define number of centers
kmeans_results <- kmeans(
      x = train_unique %>% select(LATITUDE, LONGITUDE), # only LAT & LONG
      centers = k
    )
# store your results
train_unique %<>% 
  mutate(clust_kmeans = kmeans_results$cluster)
```

Let's plot our results: 

```{r}
# plot the kmeans results 
# first add the medoids in the data
train_unique <- as_tibble(kmeans_results$centers) %>% 
  mutate(WAPs = "WAPs_kmeans") %>% 
  bind_rows(train_unique) # add the centers into the dataset
plot_kmeans <- train_unique %>% 
  ggplot(aes(x = LONGITUDE, y = LATITUDE, col = factor(clust_kmeans))) +
    geom_point() +
    geom_point(aes(x = if_else(WAPs == "WAPs_kmeans", LONGITUDE, NULL), 
                   y = if_else(WAPs == "WAPs_kmeans", LATITUDE, NULL)),
               col = "red")
# plot the results 
plot_kmeans
```

If we focus at the information by building we will be able to detect whihc are the WAPs closer to the center of our k-means:

```{r}
# show a table of the centroids
kable(
  train_unique %>% 
    filter(WAPs == "WAPs_kmeans") %>% 
    select(LATITUDE, LONGITUDE, clust_kmeans)
  ) %>%  
  kable_styling(full_width = F)
# data frame with all the centers and the correct buildings
train_unique %>%
  filter(WAPs == "WAPs_kmeans") %>%
  select(LATITUDE, LONGITUDE) %>%
  mutate(BUILDINGID = if_else(between(LONGITUDE, -7700, -7600), 0, 
                              if_else(between(LONGITUDE, -7600, -7400), 1, 2)
                              )
         ) %>% 
  arrange(BUILDINGID) %>% 
  rownames_to_column(var = "center_id") %>% 
  assign("center_b", ., envir = .GlobalEnv)
```

TO filter the WAPs that are closer to this position, first we will have to predict where is the position of each WAP:

```{r}
WAPs_pred_loc <- train_unique %>% 
  # exlclude kmeans centers
  filter(WAPs != "WAPs_kmeans") %>%
  # avoid duplicated values
  distinct(LATITUDE, LONGITUDE, WAPs) %>%
  # use the median by wap to try to predict where the WAP has more presence
  group_by(WAPs) %>% 
  summarise(LATITUDE = median(LATITUDE), 
            LONGITUDE = median(LONGITUDE))
# plot the results
WAPs_pred_loc %>% 
  ggplot(aes(x = LONGITUDE, y = LATITUDE)) +
    geom_point()
```


Now we will select the best WAPs based on the centers of the buildings. We will start by the building 0:


```{r}
# We will use only LONGITUDE as is the only variable who is not corssing the 
# other buildings
LAT_tresh <- 0 # define treshhold LATITUDE
LONG_tresh <- 1.9 # define treshhold LONGITUDE
imp_WAPs <- tibble()
for (i in 1:k) {
  temp_waps <- WAPs_pred_loc %>% 
    filter(
      between(
        x = LONGITUDE, 
        left = center_b$LONGITUDE[i] - LONG_tresh, 
        right = center_b$LONGITUDE[i] + LONG_tresh
        ) | 
      between(
        x = LATITUDE, 
        left = center_b$LATITUDE[i] - LAT_tresh, 
        right = center_b$LATITUDE[i] + LAT_tresh
        )
      ) %>% 
    distinct(WAPs, .keep_all = F) %>% 
    assign(paste0("imp_waps_center", i), ., envir = .GlobalEnv)
  
  # store your resuls in a tibble
  imp_WAPs %<>% 
    bind_rows(temp_waps) %>% 
    distinct(WAPs)
}
# where are placed the localised waps?
train_unique %>% 
  ggplot(aes(x = LONGITUDE, y = LATITUDE)) +
    geom_point() +
    geom_point(aes(
      x = if_else(WAPs %in% imp_WAPs$WAPs, LONGITUDE, NULL),
      y = if_else(WAPs %in% imp_WAPs$WAPs, LATITUDE, NULL),
    ), col = "red")
  
```

### Apply the model on the train data

Now we have the best WAPs to predict, at least, the Building: 

```{r}
train_b <- train %>% 
  select(imp_WAPs$WAPs, BUILDINGID) %>% 
  distinct_all()
```

Now we will create our train and test with caret: 

```{r}
# train and test creation 
train_id <- createDataPartition(y = train_b$BUILDINGID, 
                                p = 0.75, 
                                list = F)
training <- train_b[train_id,]
testing <- train_b[-train_id,]
```

Let's create a simple model, like a simple decision tree: 

```{r}
library(doParallel)
cl <- makeCluster(detectCores() - 1)
system.time({
  registerDoParallel(cl)
  mod <- caret::train(
    factor(BUILDINGID) ~ .,
    data = train_b, 
    method = "rf",
    ntree = 20
  )
  stopCluster(cl)
})

mod
```

Results on the test: 

```{r}
validation <- read_rds("../../data/clean/validation.rds")

confusionMatrix(data =  predict(mod, validation), 
                reference = factor(validation$BUILDINGID), 
                dnn = c("Prediction", "Reference"))
```

This results is not working properly. Bad results on validation. 
